### 2015-07-09 manuscript/defs.tex

@@

\begin{definition}
  We say an refd $r$ {\it matches} a Genome $G$ at position $i$ if, for
  all $j$ such that $r_j \neq *$, $r_j = G_{i+j}$.
\end{definition}

@@

@@

@@

The following are things I wanted to try to prove that may or may not
be useful.

\begin{lemma}
  Let $s$ be a seed, $r$ be a refd consistent with $s$,
  and $r'$ be an refd consistent with $s$ such that $|r'| < |r|$.  
\end{lemma}

>>>>

\begin{definition}
An $L$-mer is a string of length $l$.
\end{definition}

\begin{definition}
Given a spaced seed $s$ of length $l$ and an $l$-mer $x$, the {\it seeded
$l$-mer} $s'$ is created by removing all characters of $x$
corresponding to $0$'s in $s$.  Let $\sigma_s(x)$ denote the seeded
$l$-mer for $s$.
\end{definition}
Example: for $s=11011$ and $x = AACGG$, $\sigma_s(x) = AACC$.

@@

\begin{definition}
  We say an refd $r$ {\it matches} a genome $G$ at position $i$ if, for
  all $j$ such that $r_j \neq *$, $r_j = G_{i+j}$.
\end{definition}

@@

\begin{observation}
$s$ matches $r$ at $i$ if $\sigma_s(r[i:i+|s|])$ does not contain any
  $*$ symbols.
\end{observation}

$\sigma(r[3:8]) = AAGG$ (hence a match at $i=3$), but $\sigma(r[2:7])
= AA*G$ (hence no match at $i=2$).

@@

\begin{definition}
Given the refd $r$ of an elementary repeat family with set $S$, we say
that $r$ is {\it tight} if, for each $i$ such that $r_i = *$, there
exists two sequences defined by $S$ that have different bases in
position $i$.
\end{definition}
In other words: $r$ is tight if it only uses $*$ symbols where it must
to match everything sequence defined by $S$.

{\bf Comments:} I had it in mind that the algorithm would always
return a tight refd.  But in Carly's defense she gave the example:
s=11011, AAAAATCCCCC, AAGAATCCGCC, where ends up with AA*AA*AA*AA,
which is not tight.  Interestingly, if we have AAAAATTCCCCC and
AAGAATTCCGCC, then we get AA*AATTCC*CC -- to that extra T makes it
tight.  Not sure if this is significant.

\section{From Thesis}

In the following I'm going through definitions / parallels from Nate's
thesis and seeing if I can create an analgy for spaced seeds.

The following are things I wanted to try to prove that may or may not
be useful.  In all of these I'm assuming a fixed genome $G$, a fixed
frequence requriement $f$, and a fixed seed $s$ with length $l$ and
weight $w$.

\begin{lemma} 
For any $l$-mer $x$, the seeded $l$-mer $\sigma_s(x)$ can be a member
of at most $l$ different families.
\end{lemma}
My gut is that this is true, but not necessarily tight.  Maybe its
$w$, or $l-w$?

\begin{definition}
Let $x$ and $y$ be two strings such that $x = a \dot b$, $y = b \dot
c$, and $|b| = i$.  Then $x \circ_i y = a\dot b \dot c$.
\end{definition}

$AAACC \circ_2 CCGGG = AAACCGGG$.  $AAACC \circ_3 CCGGG$ is undefined.

This is a modification of Nate's $x \circ y$ operator.  May need to be
adapted for seeds.

@@
